Accelerated evolution of convective simulations

### 2018-06-13 tex/bvp_paper.tex
readthrough of sections 1 and 2 complete

Unfortunately, astrophysical convective systems are stiff in more than one 
timescale. Specifically, the Peclet number (Pe), the ratio of the thermal
diffusion timescale to the advective velocity timescale, is large.
This further stiffness arises as a result of the thermodynamic structure 
evolving over the course of thermal timescales which are much larger than
the relevant dynamical advective
timescales. In order to reach thermal equilibration, a steady state in which
the thermal structure of the atmosphere is no longer evolving over time,
many dynamical timescales must be simulated.
Transport by convection is a highly nonlinear process,
and this makes addressing the stiffness much more challenging; even fully
implicit  methods remain bound by the nonlinear flow timescales
\cite{viallet&all2011, viallet&all2013, viallet&all2016}. 
Resolving dynamics in atmospheres which are sufficiently
thermally equilibrated remains a challenging problem.
Solar convection is a prime example of this phenomenon, as
dynamical timescales in the solar convective zone are relatively short 
(convection overturns every $\sim 5$ minutes at the solar surface)
compared to the Sun's thermal evolution timescale, which is O($10^7$) years
\cite{stix2003}.  
In such a system, it is impossible to resolve the convective dynamics while also
meaningfully evolving the thermal structure of the system using
traditional timestepping techniques alone.
As modern simulations aim to model natural, high-Pe convection
in the high-Rayleigh-number (Ra) regime,
the thermal diffusion timescale ($t_{\kappa}$, defined in section \ref{sec:ae}) 
becomes intractably large compared to dynamical timescales 
such as the freefall time ($t_{\text{ff}}$, defined in section \ref{sec:experiment})
\cite{anders&brown2017}, 
\begin{equation}
\frac{t_{\kappa}}{t_{\text{ff}}} \propto (\text{Ra})^{1/2}.
\end{equation}
Furthermore, as dynamical and thermal timescales separate, 
simulations become more turbulent. Capturing appropriately resolved
turbulent motions requires finer grid meshes and smaller timesteps.
Thus, the progression of simulations into the high-Ra
regime of natural convection is slowed by two simultaneous effects: timestepping
through a single convective overturn time becomes more computationally expensive
and the number of overturn times required for systems to reach thermal equilibration
grows.

@@

In this work, we study a method of achieving accelerated evolution of
convective simulations. We couple measurements of the dynamics of unequilibrated
convective simulations with knowledge about energy balances in the desired solution
to self-consistently adjust the mean vertical thermodynamic profile towards its evolved state. 
While a technique of this kind has been used previously \cite{hurlburt&all1986},
the details of implementation, the convergence properties, and whether or not the
accelerated evolution state corresponds to a standard evolution state are not documented.
In section \ref{sec:experiment}, we describe our convective simulations and
numerical methods. In section \ref{sec:ae}, we describe the procedure for 
achieving accelerated evolution. In
section \ref{sec:results}, we compare accelerated evolution solutions
to solutions obtained from standard evolution through a full thermal diffusion timescale. Finally,
in section \ref{sec:extensions}, we offer concluding remarks and
discuss extensions of the methods presented here.

@@

Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal, periodic) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  
We study 2D and 3D convection in which the domain is a cartesian box, 
whose dimensionless vertical extent is $z \in [0, 1]$, 
and which is horizontally periodic with an extent of $x, y \in [0, \Gamma]$,
where $\Gamma = 2$ is the aspect ratio, as has been previously studied
\cite{goluskin&all2014, johnston&doering2009}. 
In 2D simulations, we set $v = \partial_y = 0$.
We specify no-slip, impenetrable boundary conditions at both the top and
bottom boundary,
\begin{equation}
u = v = w = 0 \, \, \text{at}\,\,z = \pm 0,1,
\label{eqn:vel_bcs}
\end{equation}
and we use mixed thermal boundary conditions, such that
\begin{equation}
T_1 = 0 \,\,\text{at}\,\, z=1, \qquad
\frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=0.
\label{eqn:temp_bcs}
\end{equation}
For this choice of boundary conditions, the critical value of Ra at which
the onset of convection occurs is Ra$_{\text{crit}} = 1295.78$ \cite{goluskin2016}, and the
supercriticality of a run is defined as $S \equiv \text{Ra}/\text{Ra}_{\text{crit}}$.
Studies of convection which aim to model
astrophysical systems such as stars often employ mixed thermal
boundary conditions, as we do here \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.
Our choice of the thermal boundary conditions in Eqn.~(\ref{eqn:temp_bcs}) 
was motivated by the fact that accelerated evolution is simpler when both the
thermal profile and the flux through the domain are fixed at a boundary 
(see section \ref{sec:ae}).

@@

We study in depth a 2D simulation at $S = 10^5$ to demonstrate the power of AE.
We compare kinetic energy (KE, black line) and mean temperature (blue line)
traces from a SE run in Fig.~\ref{fig:time_trace}a to an AE run
in Fig.~\ref{fig:time_trace}c.
In Fig.~\ref{fig:time_trace}a, the time evolution of the SE simulation is shown.
The KE grows exponentially from white noise during the
first $\sim 25$ $t_{\text{ff}}$. The solution then saturates and begins to slowly
equilibrate towards the proper isothermal profile in the interior of the domain.
This slow equilibration is evident in the behavior of the blue line, which measures
$\angles{T} - T_{\text{top}}$, where \angles{T} is the volume-average of $T$, and
$T_{\text{top}} = -0.5$ is the temperature at the upper boundary.
The mean atmospheric temperature and
kinetic energies are fully converged when $t = 4000$ $t_{\text{ff}}$ $= 0.35$ $t_{\kappa}$.
We show roughly the first thousand freefall time
units of evolution, as well as the evolved thermodynamic state reached after a full
thermal time of evolution.  In Fig.~\ref{fig:time_trace}c, similar traces are
shown for the corresponding AE solution
at the same parameters. The same linear growth phase occurs, but shortly after
the peak of convective transient we accelerate the convergence of the atmosphere
through the process which we describe below. We adjust the 1D vertical profile of
the atmosphere three times, as denoted by the three labeled
arrows in the graph numbered 1-3.  After the third profile adjustment, we find that
the atmosphere is nearly in its converged state and we begin to sample the evolved
convective dynamics.

The horizontally averaged profiles of the vertical conductive flux, 
F$_{\kappa} = \angles{-\kappa\grad(T_0 + T_1)}_{x,y}$, and the vertical convective enthalpy flux,
F$_{\text{E}} = \angles{w(T_0 + T_1)}_{x,y}$, are the basis of the AE method.
Here we use $\angles{}_{x,y}$ to represent a horizontal average. We measure
both of these fluxes early in a simulation, retrieving profiles such as
those shown in Fig.~\ref{fig:time_trace}b.
As the atmosphere evolves towards
the isothermal profile specified by the upper (cold) boundary condition, excess
temperature throughout the atmosphere must leave the domain. This excess thermal
energy leaves through the upper boundary, as seen in 
Fig.~\ref{fig:time_trace}b, where the amount of flux exiting at the top of the domain
is nearly 20 times larger the flux entering the bottom of the domain. Once the atmospheric
temperature profile reaches its evolved state, the flux entering the bottom boundary
is equal to the flux exiting through the upper boundary.  In general, this 
evolution is slow in SE (Fig.~\ref{fig:time_trace}a), but AE (Fig.~\ref{fig:time_trace}c)
can rapidly advance a system whose fluxes are in a strongly disequilibrium state (Fig.~\ref{fig:time_trace}b),
into a near-equilibrium state, as shown in Fig.~\ref{fig:time_trace}d. In
this final state both boundaries conduct the same amount of flux.
The converged state achieved through AE is at most 5\% different from the SE solution, 
as shown in Fig.~\ref{fig:time_trace}e. 
This is a very small difference considering the short timescales on which convergence
is reached and the strongly disequilibrium state used to inform the AE process.

@@

In order to adjust the temperature profle to achieve AE, we calculate the total flux,
F$_{\text{tot}} =$ F$_{\text{E}}$ + F$_{\kappa}$, and then derive the profiles
\begin{equation}
f_{\text{E}}(z) = \frac{\text{F}_{\text{E}}}{\text{F}_{\text{tot}}},\qquad
f_{\kappa}(z) = \frac{\text{F}_{\kappa}}{\text{F}_{\text{tot}}},
\label{eqn:bvp_ratios}
\end{equation}
which have the systematic asymmetries (Fig.~\ref{fig:time_trace}b) removed. These profiles describe which
parts of the atmosphere depend on convection to carry flux (where $f_{\text{E}}(z) = 1$
and $f_{\kappa}(z) = 0$).
We presume that the early convection occupies roughly the same volume as the evolved
convection, and thus that the extent of the early thermal boundary layers 
(where $f_{\kappa}(z) = 1$ and $f_{\text{E}}(z) = 0$) 
will not change significantly over the course of the atmosphere's evolution.
Under this assumption, in order to reach the converged state, 
the flux through the atmosphere must be decreased by some amount,
\begin{equation}
\xi(z,t) \equiv \frac{\text{F}_{\text{B}}}{\text{F}_{\text{tot}}},
\label{eqn:xi}
\end{equation}
where $\text{F}_{\text{B}} = \mathcal{P}$ is the amount of flux that enters the
bottom of the atmosphere. $\xi$ is a general depth-dependent scaling factor which
tells us roughly how much larger F$_\text{E}$ is in the interior than it should
be in the thermally equilibrated state.

In a time-stationary state, the horizontal- and time-average of
Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms which
vanish due to symmetry, are
\begin{gather}
\frac{\partial}{\partial z}\angles{\varpi}_{x,y} - \angles{T_1}_{x,y}\hat{z} = \angles{\bm{u}\times\bm{\omega}}_{x,y, \text{ ev}},
	\label{eqn:bouss_BVP_momentum}
\\
\frac{\partial}{\partial z}\text{F}_{\text{E, ev}} - \mathcal{P}\frac{\partial^2}{\partial z^2} \angles{T_1}_{x,y} = 0.
	\label{eqn:bouss_BVP_energy}
\end{gather}
Here, we construct $\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}} =
\xi(z) \angles{\bm{u}\times\bm{\omega}}_{x, y}$ and $\text{F}_{\text{E, ev}} = \xi(z) \text{F}_{\text{E}}$
from our unevolved state, and solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
Convective flows
are perturbations around a thermal profile defined by these equations in the proper evolved, 
statistically stationary state. Furthermore, under the proper specification of
F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$,
\emph{the mean thermodynamic structure of the system is fully specified}. 
Our choice of fixing the temperature at the top boundary and the flux at the bottom
boundary ensures that there is a unique solution for $T_1$ given the evolved
fluxes. If flux were fixed at both boundaries, there would be infinitely many
temperature solutions. If temperature were fixed at both boundaries, 
$\text{F}_{\text{B}}$ would not be precisely known \emph{a priori}.

Thus, the AE method occurs in the following steps. First, we pause a convective simulation and
construct $\xi(z)$ from measured flux profiles in the convective domain.
We solve a 1D boundary value problem consisting of
Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
to obtain an evolved thermodynamic profile, and its corresponding conductive flux.
To consistently modify the convective enthalpy flux, we multiply both the velocity field,
$\bm{u}$, and the temperature perturbations around the mean profile, $T - \angles{T}_{x,y}$,
by $\sqrt{\xi}$; this diminishes the magnitude of these perturbations, and the
flux they carry, appropriately. This scaling of variables with $\sqrt{\xi}$ is also
the reason that we multiply $\angles{\bm{u}\times\bm{\omega}}_{x, y}$ by $\xi$
before solving for the evolved temperature profile.
After adjusing the fields of a simulation in this manner, we continue timestepping forward.
For specifics on the precise implementation of the AE method, we refer
the reader to appendix \ref{appendix:recipe}.

>>>>

Unfortunately, astrophysical convective systems are stiff in more than one 
timescale. Specifically, the Peclet number (Pe), the ratio of the thermal
diffusion timescale to the convective velocity timescale, is large.
In a high Pe system, many convective dynamical timescales must pass before 
the domain reaches thermal equilibrium, a steady state in which
evolution of the thermal structure of the convective region has ceased.
Fully implicit methods cannot be used to address the stiffness resulting from
the discrepancy between convective and thermal timescales; convective flows are
highly nonlinear, and implicit methods are bound by the nonlinear flow timescales
\cite{viallet&all2011, viallet&all2013, viallet&all2016}.

Resolving dynamics in atmospheres which are sufficiently
thermally equilibrated remains a challenging problem.
Solar convection is a prime example of this phenomenon, as
dynamical timescales in the solar convective zone are relatively short 
(convection overturns every $\sim 5$ minutes at the solar surface)
compared to the Sun's thermal evolution timescale, which is O($10^7$) years
\cite{stix2003}.  
In such a system, it is impossible to resolve the convective dynamics while also
meaningfully evolving the thermal structure of the system using
traditional timestepping techniques alone.
As modern simulations aim to model natural, high-Pe convection
in the high-Rayleigh-number (Ra) regime,
the thermal diffusion timescale ($t_{\kappa}$, defined in section \ref{sec:ae}) 
becomes intractably large compared to dynamical timescales 
such as the freefall time ($t_{\text{ff}}$, defined in section \ref{sec:experiment})
\cite{anders&brown2017}, 
\begin{equation}
\frac{t_{\kappa}}{t_{\text{ff}}} \propto (\text{Ra})^{1/2}.
\end{equation}
Furthermore, as dynamical and thermal timescales separate, 
simulations become more turbulent. Capturing appropriately resolved
turbulent motions requires finer grid meshes and smaller timesteps.
Thus, the progression of simulations into the high-Ra
regime of natural convection is slowed by two simultaneous effects: timestepping
through a single convective overturn time becomes more computationally expensive
and the number of overturn times required for systems to reach thermal equilibration
grows.

@@

In this work, we study a method of achieving accelerated evolution of
convective simulations. We couple measurements of the dynamics of unequilibrated
convective simulations with knowledge about energy balances in the desired solution
to self-consistently adjust the mean vertical thermodynamic profile towards its evolved state. 
While a technique of this kind has been used previously \cite{hurlburt&all1986},
the details of implementation, the convergence properties, and whether or not the
accelerated evolution state corresponds to a standard evolution state are not documented.
In section \ref{sec:experiment}, we describe our convective simulations and
numerical methods. In section \ref{sec:ae}, we describe the procedure for 
achieving accelerated evolution. In
section \ref{sec:results}, we compare accelerated evolution solutions
to solutions obtained from standard evolution through a full thermal diffusion timescale. 
In section \ref{sec:speedups}, we compare the numerical cost of accelerated
solutions to solutions that are evolved through a thermal diffusion timescale.
Finally,
in section \ref{sec:extensions}, we offer concluding remarks and
discuss extensions of the methods presented here.

@@

Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal, periodic) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.  
We study 2D and 3D convection in which the domain is a cartesian box, 
whose dimensionless vertical extent is $z \in [0, 1]$, 
and which is horizontally periodic with an extent of $x, y \in [0, \Gamma]$,
where $\Gamma = 2$ is the aspect ratio, as has been previously studied
\cite{goluskin&all2014, johnston&doering2009}. 
In 2D simulations, we set $v = \partial_y = 0$.
We specify no-slip, impenetrable boundary conditions at both the top and
bottom boundary,
\begin{equation}
u = v = w = 0 \, \, \text{at}\,\,z = 0,1.
\label{eqn:vel_bcs}
\end{equation}
The temperature is fixed at the top boundary, and the flux is fixed at the
bottom boundary, such that
\begin{equation}
T_1 = 0 \,\,\text{at}\,\, z=1, \qquad
\frac{\partial T_1}{\partial z} = 0\,\,\text{at}\,\,z=0.
\label{eqn:temp_bcs}
\end{equation}
For this choice of boundary conditions, the critical value of Ra at which
the onset of convection occurs is Ra$_{\text{crit}} = 1295.78$ \cite{goluskin2016}, and the
supercriticality of a run is defined as $S \equiv \text{Ra}/\text{Ra}_{\text{crit}}$.
Studies of convection which aim to model
astrophysical systems such as stars often employ mixed thermal
boundary conditions, as we do here \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.
Our choice of the thermal boundary conditions in Eqn.~(\ref{eqn:temp_bcs}) 
was motivated by the fact that accelerated evolution is simpler when both the
thermal profile and the flux through the domain are fixed at a boundary 
(see section \ref{sec:ae}).

@@

We study in depth a 2D simulation at $S = 10^5$ to demonstrate the power of AE.
We compare kinetic energy (KE, black line) and mean temperature (blue line)
traces from a SE run in Fig.~\ref{fig:time_trace}a to an AE run
in Fig.~\ref{fig:time_trace}c.
In Fig.~\ref{fig:time_trace}a, the time evolution of the SE simulation is shown.
The KE grows exponentially from white noise during the
first $\sim 25$ $t_{\text{ff}}$. The solution then saturates and begins to slowly
equilibrate towards the proper isothermal profile in the interior of the domain.
This slow equilibration is evident in the behavior of the blue line, which measures
$\angles{T} - T_{\text{top}}$, where \angles{T} is the volume-average of $T$, and
$T_{\text{top}} = -0.5$ is the temperature at the upper boundary.
The mean atmospheric temperature and
kinetic energies are fully converged when $t = 4000$ $t_{\text{ff}}$ $= 0.35$ $t_{\kappa}$.
We show roughly the first thousand freefall time
units of evolution, as well as the evolved thermodynamic state reached after a full
thermal time of evolution.  In Fig.~\ref{fig:time_trace}c, similar traces are
shown for the corresponding AE solution
at the same parameters. The same linear growth phase occurs, but shortly after
the peak of convective transient we accelerate the convergence of the atmosphere
through the process which we describe below. We adjust the 1D vertical profile of
the atmosphere three times, as denoted by the three labeled
arrows in the graph numbered 1-3.  The third profile adjustment associated with
arrow 3 is small enough (see appendix \ref{appendix:recipe}) that we assume
the atmosphere is sufficiently converged, and we begin to sample the evolved
convective dynamics.

The horizontally averaged profiles of the vertical conductive flux, 
F$_{\kappa} = \angles{-\kappa\grad(T_0 + T_1)}_{x,y}$, and the vertical convective enthalpy flux,
F$_{\text{E}} = \angles{w(T_0 + T_1)}_{x,y}$, are the basis of the AE method.
Here we use $\angles{}_{x,y}$ to represent a horizontal average. We measure
both of these fluxes early in a simulation, retrieving profiles such as
those shown in Fig.~\ref{fig:time_trace}b.
As the atmosphere evolves towards
the isothermal profile specified by the upper (cold) boundary condition, excess
temperature throughout the atmosphere must leave the domain. This excess thermal
energy leaves through the upper boundary, as seen in 
Fig.~\ref{fig:time_trace}b, where the amount of flux exiting at the top of the domain
is nearly 20 times larger the flux entering the bottom of the domain. Once the atmospheric
temperature profile reaches its evolved state, the flux entering the bottom boundary
is equal to the flux exiting through the upper boundary.  In general, this 
evolution is slow in SE (Fig.~\ref{fig:time_trace}a), but AE (Fig.~\ref{fig:time_trace}c)
can rapidly advance a system whose fluxes are in a strongly disequilibrium state (Fig.~\ref{fig:time_trace}b),
into a near-equilibrium state, as shown in Fig.~\ref{fig:time_trace}d. In
this final state both boundaries conduct the same amount of flux.
The converged fluxes achieved through AE is at most 5\% different from the SE solution, 
as shown in Fig.~\ref{fig:time_trace}e. 
This is a very small difference considering the short timescales on which convergence
is reached and the strongly disequilibrium state used to inform the AE process.

@@

In order to adjust the temperature profile to achieve AE, we calculate the total flux,
F$_{\text{tot}} =$ F$_{\text{E}}$ + F$_{\kappa}$, and then derive the profiles
\vspace{-0.5cm}
\begin{equation}
f_{\text{E}}(z) = \frac{\text{F}_{\text{E}}}{\text{F}_{\text{tot}}},\qquad
f_{\kappa}(z) = \frac{\text{F}_{\kappa}}{\text{F}_{\text{tot}}},
\label{eqn:bvp_ratios}
\end{equation}
which have the systematic asymmetries (Fig.~\ref{fig:time_trace}b) removed. These profiles describe which
parts of the atmosphere depend on convection to carry flux (where $f_{\text{E}}(z) = 1$
and $f_{\kappa}(z) = 0$).
We presume that the early convection occupies roughly the same volume as the evolved
convection, and thus that the extent of the early thermal boundary layers 
(where $f_{\kappa}(z) = 1$ and $f_{\text{E}}(z) = 0$) 
will not change significantly over the course of the atmosphere's evolution.
Under this assumption, in order to reach the converged state, 
the flux through the atmosphere must be decreased by some amount,
\vspace{-0.5cm}
\begin{equation}
\xi(z,t) \equiv \frac{\text{F}_{\text{B}}}{\text{F}_{\text{tot}}},
\label{eqn:xi}
\end{equation}
where $\text{F}_{\text{B}} = \mathcal{P}$ is the amount of flux that enters the
atmosphere at the bottom, fixed-flux boundary.
$\xi$ is a general depth-dependent scaling factor which
tells us roughly how much larger F$_\text{E}$ is in the interior than it should
be in the thermally equilibrated state (e.g., in Fig.~\ref{fig:time_trace}b,
F$_{\text{tot}} \sim$ F$_{\text{E}} \sim 15\mathcal{P}$ just below the upper boundary layer, 
but in the equilibrated state 
it should just be $\mathcal{P}$, so $\xi \sim 1/15$ at that depth).

In a time-stationary state, the horizontal- and time-average of
Eqns.~(\ref{eqn:bouss_momentum}) and (\ref{eqn:bouss_energy}), neglecting terms which
vanish due to symmetry, are
\vspace{-0.5cm}
\begin{gather}
\frac{\partial}{\partial z}\angles{\varpi}_{x,y} - \angles{T_1}_{x,y}\hat{z} = \angles{\bm{u}\times\bm{\omega}}_{x,y, \text{ ev}},
	\label{eqn:bouss_BVP_momentum}
\\
\frac{\partial}{\partial z}\text{F}_{\text{E, ev}} - \mathcal{P}\frac{\partial^2}{\partial z^2} \angles{T_1}_{x,y} = 0.
	\label{eqn:bouss_BVP_energy}
\end{gather}
Here, we construct $\angles{\bm{u}\times\bm{\omega}}_{x, y,\text{ ev}} =
\xi(z) \angles{\bm{u}\times\bm{\omega}}_{x, y}$ and $\text{F}_{\text{E, ev}} = \xi(z) \text{F}_{\text{E}}$
from our unevolved state, and solve for $\angles{\varpi}_{x,y}$ and $\angles{T_1}_{x,y}$.
Convective flows
are perturbations around a thermal profile defined by these equations in the proper evolved, 
statistically stationary state. Furthermore, under the proper specification of
F$_{\text{conv, ev}}$ and $\angles{\bm{u}\times\bm{\omega}}_{x,y\text{, ev}}$,
\emph{the mean thermodynamic structure of the system is fully specified}. 
Our choice of fixing the temperature at the top boundary and the flux at the bottom
boundary ensures that there is a unique solution for $T_1$ given the evolved
fluxes. If flux were fixed at both boundaries, there would be infinitely many
temperature solutions. If temperature were fixed at both boundaries, 
$\text{F}_{\text{B}}$ would not be precisely known \emph{a priori}.

Thus, the AE method occurs in the following steps. First, we pause a convective simulation and
construct $\xi(z)$ from measured flux profiles in the convective domain.
We solve a 1D boundary value problem (BVP) consisting of
Eqns.~(\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy})
to obtain an evolved thermodynamic profile, and its corresponding conductive flux.
As the AE BVP solve only adjusts $\angles{T}$ and $\angles{\varpi}$, we must
also appropriately adjust the temperature perturbations around the mean and the
convective velocity flows, or else F$_{\text{E}}$ would be left unchanged, and
would still be in a strongly disequilibrium state (e.g., Fig.~\ref{fig:time_trace}b).
To consistently modify the convective enthalpy flux, we multiply both the velocity field,
$\bm{u}$, and the temperature perturbations around the mean profile, $T - \angles{T}_{x,y}$,
by $\sqrt{\xi}$; this diminishes the magnitude of these perturbations, and the
flux they carry, appropriately. This scaling of variables with $\sqrt{\xi}$ is also
the reason that we multiply $\angles{\bm{u}\times\bm{\omega}}_{x, y}$ by $\xi$
to construct $\angles{\bm{u}\times\bm{\omega}}_{x, y\text{, ev}}$.
After adjusing the fields of a simulation in this manner, we continue timestepping forward.
For specifics on the precise implementation of the AE method, we refer
the reader to appendix \ref{appendix:recipe}.
